\documentclass[a4paper,12pt]{article}

%A Few Useful Packages
\usepackage{marvosym}
\usepackage{fontspec} 					%for loading fonts
\usepackage{xunicode,xltxtra,url,parskip} 	%other packages for formatting
\RequirePackage{color,graphicx}
\usepackage[usenames,dvipsnames]{xcolor}
%\usepackage[big]{layaureo} 				%better formatting of the A4 page
\usepackage{fullpage}			%better formatting of the A4 page
% an alternative to Layaureo can be ** \usepackage{fullpage} **
\usepackage[a4paper, total={7.4in, 10in}]{geometry}
\usepackage{supertabular} 				%for Grades
\usepackage{titlesec}					%custom \section
\usepackage{fontawesome}                %icons

\usepackage{multirow}

\usepackage{paralist} % for horizontal bullet points
\usepackage[inline]{enumitem} % load package

\usepackage{longtable} % for the work experience section allowing page breaks

%Setup hyperref package, and colours for links
\usepackage{hyperref}
\definecolor{linkcolour}{rgb}{0,0.2,0.7}
\hypersetup{colorlinks,breaklinks,urlcolor=linkcolour, linkcolor=linkcolour}

%FONTS
\defaultfontfeatures{Mapping=tex-text}
%\setmainfont[SmallCapsFont = Fontin SmallCaps]{Fontin}
%%% modified for Karol Kozioł for ShareLaTeX use
\setmainfont[
SmallCapsFont = Fontin-SmallCaps.ttf,
BoldFont = Fontin-Bold.ttf,
ItalicFont = Fontin-Italic.ttf
]
{Fontin-Regular.ttf}
%%%

%CV Sections inspired by:
%http://stefano.italians.nl/archives/26
\titleformat{\section}{\Large\scshape\raggedright}{}{0em}{}[\titlerule]
\titlespacing{\section}{0pt}{3pt}{3pt}
%Tweak a bit the top margin
\addtolength{\voffset}{1cm}

%Italian hyphenation for the word: ''corporations''
\hyphenation{im-pre-se}

%-------------WATERMARK TEST [**not part of a CV**]---------------
\usepackage[absolute]{textpos}

\setlength{\TPHorizModule}{30mm}
\setlength{\TPVertModule}{\TPHorizModule}
\textblockorigin{2mm}{0.65\paperheight}
\setlength{\parindent}{0pt}

\setlist[itemize]{itemsep=0pt, topsep=0pt}

%--------------------BEGIN DOCUMENT----------------------
\begin{document}

\pagestyle{empty} % non-numbered pages

\font\fb=''[cmr10]'' %for use with \LaTeX command

%--------------------TITLE-------------
\par{
    \centering{\LARGE Bruno \textsc{Campera}}\\
    %\medskip\\
    \textcolor{white}{\tiny\textbf{Summary}}\\
    %\centering{\normalsize Backend Software Engineer with a passion for highly scalable and maintainable code. Over 7 years of experience in the IT industry, including working with international teams.}
    \centering{\normalsize Backend Software Engineer specializing in Java, AWS, Spring Boot, and Quarkus, with a passion for building highly scalable and maintainable systems. Over 7 years of experience in the technology field, including collaboration with international teams to deliver robust solutions.}

\par}

%--------------------SECTIONS-----------------------------------
%Section: Personal Data

% \begin{table}[h]
% \centering
% \begin{tabular}{rlrl}
% \textsc{Email:}     & brunoc@alunos.utfpr.edu.br
%     & {Links:} & \href{https://www.linkedin.com/in/bruno-campera-288b0b77/}{\faLinkedinSquare\ LinkedIn}  \href{https://github.com/brunocmpr}{\faGithubSquare\ GitHub} \\
% \textsc{Location:} & Curitiba/PR, Brazil.
%     & \textsc{Phone number:}     & \href{https://api.whatsapp.com/send?phone=5541996658096}{\faWhatsapp\ +55~41~99665~8096}\\
% \end{tabular}
% \end{table}
\noindent\makebox[\textwidth]{
\begin{tabular}{rlrl}
\textsc{Email:}     & brunoc@alunos.utfpr.edu.br
    & \textsc{Links:} & \href{https://www.linkedin.com/in/bruno-campera-288b0b77/}{\faLinkedinSquare\ LinkedIn}  \href{https://github.com/brunocmpr}{\faGithubSquare\ GitHub} \\
\textsc{Location:} & Curitiba/PR, Brazil.
    & \textsc{Phone number:}     & \href{https://api.whatsapp.com/send?phone=5541996658096}{\faWhatsapp\ +55~41~99665~8096}\\
\end{tabular}
}

%Section: Work Experience at the top

\section{Technical Skills}
\vspace{2pt}
\begin{tabular}{rp{15.2cm}}
\raggedleft Programming:
% & Backend development with REST APIs in Java and Spring Boot, unit testing using JUnit and Mockito. Integration with PostgreSQL database and usage of SQL. Source code version control with Git. Mobile development in Dart and Flutter. Frontend development with HTML, CSS, JavaScript, Typescript, and Angular. Previous experience with development of embedded systems in C++, Qt 5, and QML.\\
& \begin{itemize*}[label=\Large\textbullet] %[label=\Large\textbullet, itemjoin={, }, itemjoin*={ and }]
    \item Java
    \item Javascript
    \item Dart
    \item RESTful API development
\end{itemize*}\\
\raggedleft Frameworks:
& \begin{itemize*}[label=\Large\textbullet]
    \item Spring Boot
    \item Quarkus
    \item Flutter
\end{itemize*}\\
\raggedleft Cloud:
& \begin{itemize*}[label=\Large\textbullet]
    \item AWS
\end{itemize*}\\
\raggedleft Database and ORM:
& \begin{itemize*}[label=\Large\textbullet]
    \item PostgreSQL
    \item MySQL
    \item Hibernate
    \item Spring Data JPA
    \item Panache
\end{itemize*}\\
\raggedleft Other Tools:
& \begin{itemize*}[label=\Large\textbullet]
    \item JUnit 5
    \item Mockito
    \item Linux
    \item Git
\end{itemize*}\\
\raggedleft Processes:
& \begin{itemize*}[label=\Large\textbullet]
    \item Agile methodologies, mainly Scrum and Kanban
\end{itemize*}\\
\raggedleft Languages:
% &Fluent in English, Native Brazilian Portuguese
& \begin{itemize*}[label=\Large\textbullet]
    \item English (C1 Advanced)
    \item Native Brazilian Portuguese
\end{itemize*}\\
\end{tabular}

\section{Work Experience}

\vspace{8pt}

\textbf{\textsc{Software Engineer}} at \textbf{Stoneridge} \hfill \textit{07/2024 -- Current}

{\small
\begin{itemize}[leftmargin=*,label=\large\textbullet]
    \setlength\itemsep{-0.2em}
    \item Developed and maintained RESTful APIs on the backend with Java 17 and Spring, hosted on AWS EC2.
    \item Created AWS Lambdas for serverless applications with Java 21 and Quarkus.
    \item Developed unit tests using JUnit 5 and Mockito.
    \item Interfaced with AWS Kinesis for device intercommunication and AWS DynamoDB for message storage.
    \item Modeled and implemented MySQL database schema using SQL.
    \item Employed usage of Hibernate for modelling entities and managing persistence.
    \item Used Git for version control.
\end{itemize}
}

\textbf{\textsc{Software Engineer}} at \textbf{FS Tech} \hfill \textit{12/2023 -- 12/2024}

{\small
\begin{itemize}[leftmargin=*,label=\large\textbullet]
    \setlength\itemsep{-0.2em}
    \item Developed RESTful APIs on the backend with Java 17 and Quarkus.
    \item Modeled and implemented a PostgreSQL database schema using SQL.
    \item Employed usage of Hibernate ORM and Panache for database interaction, along with JPQL and Native SQL.
    \item Integrated Hibernate Envers for auditing and versioning of database entities.
    \item Used Git for version control.
\end{itemize}
}

\textbf{\textsc{Software Engineer}} at \textbf{Federal Data Processing Service (SERPRO)} \hfill \textit{09/2021 -- 09/2023}

{\small
\begin{itemize}[leftmargin=*,label=\large\textbullet]
    \setlength\itemsep{-0.2em}
    \item Worked on the development of the Compras.gov.br procurement platform.
    \item Developed RESTful APIs on the backend using Java 17 and Spring Boot 3.
    \item Modeled and implemented a PostgreSQL database schema using SQL.
    \item Interacted with database through Spring Data JPA and Hibernate ORM, along with JPQL.
    \item Contributed to the development of a Single Page Application (SPA) using Angular, HTML, CSS, and Typescript.
    \item Collaborated in an Agile team following Scrum.
    \item Used Git for version control.
\end{itemize}
}

\textbf{\textsc{Embedded Software Engineer}} at \textbf{Alta Rail Technology} \hfill \textit{02/2021 -- 08/2021}

{\small
\begin{itemize}[leftmargin=*,label=\large\textbullet]
    \setlength\itemsep{-0.2em}
    \item Worked on the development of an embedded application for railway trains.
    \item Developed modules in C++ for a distributed application.
    \item Used Google's FlatBuffers library for serialization and module intercommunication.
    \item Used Git for version control.
\end{itemize}
}

\textbf{\textsc{Embedded Software Engineer}} at \textbf{Agres Sistemas Eletrônicos} \hfill \textit{06/2019 -- 01/2021}

{\small
\begin{itemize}[leftmargin=*,label=\large\textbullet]
    \setlength\itemsep{-0.2em}
    \item Contributed to the development of an embedded application for farm tractors.
    \item Conducted interviews and gathered application requirements.
    \item Developed a C++ application using the Qt 5 framework.
    \item Enhanced the object-oriented architecture by applying SOLID principles.
    \item Designed the user interface with QML following the MVC pattern.
    \item Collaborated in an Agile team following Scrum.
    \item Used Git for version control.
\end{itemize}
}

\textbf{\textsc{Software Engineer}} at \textbf{ExxonMobil BSC Brasil} \hfill \textit{11/2017 -- 06/2019}

{\small
\begin{itemize}[leftmargin=*,label=\large\textbullet]
    \setlength\itemsep{-0.2em}
    \item Contributed to the development of ABAP programs for the SAP ERP platform.
    \item Developed and maintained SAP ABAP reports.
    \item Created editable forms using SAP Smartforms and Adobe's SAP Interactive Forms technologies.
    \item Developed small utility web applications with HTML, CSS and JavaScript.
    \item Independently created scripts that automated manual processes in forms, saving hundreds of hours.
\end{itemize}
}
%Section: Education
\section{Education}
\vspace{6pt}
\begin{tabular}{rl}

\rule{2cm}{0pt} 2023 & \textsc{Agile Software Development} specialization \\ &\normalsize\textbf{Federal University of Paraná (UFPR)}, Curitiba-PR\\&\\
2017 & \textsc{Computer Engineering} degree \\ &\normalsize\textbf{Federal University of Technology – Paraná (UTFPR)}, Curitiba-PR\\&\\
% 2009 & \textsc{Computer Technician} course \\ &\normalsize\textbf{Escola Técnica Estadual de São Paulo (ETESP)}, São Paulo-SP
\end{tabular}

\end{document}
